---
layout : post
title: "Shelter Animal Outcomes"
author: "ooDoo"
date: 2017-04-11
categories : kaggle
cover : /assets/article_images/title/instacode_sizedown.png
---

# 0. SETTING
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# basic package
library(ggplot2)
library(ggthemr)
library(lubridate)
library(readr)
library(stringr)
library(dplyr)

# setwd
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/0. Kaggle/4. Shelter Animal Outcomes/9)Data")
```


# 1. DATA IMPORT
```{r}
train <- read_csv("train.csv")
test <- read_csv("test.csv")
#sample_submission <- read_csv("sample_submission.csv")
#head(sample_submission)
#rm(sample_submission)
```

##1) DATA CHECK 
```{r}
# train
head(train)
names(train)

# test
head(test)
names(test)
```
- target variables is only "OutcomeType" 

##2) DATA EXPLORATION
```{r}
# Check Object variable
unique(train$OutcomeType)
unique(train$OutcomeSubtype)
# Check what is "Transfer"
unique(train$OutcomeSubtype[train$OutcomeType == "Transfer"])
train%>%
    filter(OutcomeType == "Transfer") %>%
    select(OutcomeSubtype) %>%
    group_by(OutcomeSubtype)%>%
    summarise(count = n())
```

```{r}
# Check the others
unique(train$AnimalType)
unique(train$SexuponOutcome) # Sex and whether Neutered or not
table(train$SexuponOutcome)  # don't count number using "length" function. it counts 1 more number, since name row
unique(train$AgeuponOutcome) # it needs to set the same measure to month 
table(train$AgeuponOutcome) # it needs to set the same measure to month 

length(unique(train$Breed)) # the number of breed is 1380
length(unique(train$Color)) # the number of color is 366

head(train)
#View(train)
#View(test)
```
*in AgeupounOutcome it needs to set the same measure to day*
*in color and Breed, it needs to classfy higer levels*



#2. FEATURE HANDLING
##1) AGE_STR EXTRACT
```{r}
Str_Function <- function(x){
    ifelse(str_split(x, "[ ]")[[1]][2] == "day" | str_split(x, "[ ]")[[1]][2] == "days", as.numeric(str_split(x, "[ ]")[[1]][1]),
        ifelse(str_split(x, "[ ]")[[1]][2] == "week" | str_split(x, "[ ]")[[1]][2] == "weeks", as.numeric(str_split(x, "[ ]")[[1]][1]) * 7,
            ifelse(str_split(x, "[ ]")[[1]][2] == "month" | str_split(x, "[ ]")[[1]][2] == "months", as.numeric(str_split(x, "[ ]")[[1]][1]) * 30,
                ifelse(str_split(x, "[ ]")[[1]][2] == "year" | str_split(x, "[ ]")[[1]][2] == "years", as.numeric(str_split(x, "[ ]")[[1]][1]) * 365,
                    ifelse(x == "0 years", 350, NA)))))
    }
```

###(1) APPLY STR_FUCTION
```{r}
# apply Str_Fuction to train
train$AGE <- NULL
train$AGE <- sapply(train$AgeuponOutcome, FUN = Str_Function)
table(is.na(train$AGE))

# apply Str_Fuction to test
test$AGE <- NULL
test$AGE <- sapply(test$AgeuponOutcome, FUN = Str_Function)
```
*but there is still 84 NAs in "Ageuponoutcom" variable*

###(2) INTERPOLATE INFORMATION
```{r}
# Check NA's feature
## Train
train%>%
    dplyr::select(-c(AnimalID, DateTime)) %>%
    filter(is.na(AGE) == TRUE)

## TEST
test%>%
    filter(is.na(AGE) == TRUE)
```
*: NA of AGE's feature*
 - 2016.02
 - almost is cat and transfer

```{r}
# Check distribution
train%>%
    mutate(Income_Year = year(DateTime),
    Income_Month = month(DateTime),
    Income_Day = day(DateTime))%>%
    filter(Income_Year == 2016 & Income_Month == 2,
           Breed == "Domestic Shorthair Mix",
           is.na(AGE) == FALSE,
           AnimalType == "Cat") %>%    
    ggplot(aes(x = OutcomeType, y = AGE, color = OutcomeType)) +
    geom_boxplot() +
    geom_point()

# Check dietail value for interpolation
train%>%
    mutate(Income_Year = year(DateTime),
    Income_Month = month(DateTime),
    Income_Day = day(DateTime))%>%
    filter(Income_Year == 2016 & Income_Month == 2,
           Breed == "Domestic Shorthair Mix",
           is.na(AGE) == FALSE,
           AnimalType == "Cat") %>%    
    group_by(OutcomeType)%>%
    summarise(Mid = median(AGE))
    #summarise(Mean = mean(AGE)) 
```
*i'm gonna using median, since there is a huge outlier in train case.*

###(3) AGE INTERPOLATE
```{r}
# train
train$AGE[is.na(train$AGE) == "TRUE"] <- 730 
table(is.na(train$AGE))

# test
test$AGE[is.na(test$AGE) == "TRUE"] <- 730 
table(is.na(test$AGE))
unique(train$SexuponOutcome)
```

##2) FEATURE EXTRACT
```{r}
FeatureExtract <- function(data){
    data%>%
        # Date Varible
        mutate(Income_Year = year(DateTime),
               Income_Month = as.factor(month(DateTime)),
               Income_Day = day(DateTime)) %>%
        # Change AGE variable as numeric 
        mutate(AGE = as.numeric(AGE))%>%
        # Name and SexuponOutcome Dummy
        mutate(Name = ifelse(is.na(Name)== FALSE , "N_O", "N_X"),
               Neutered_Dummy = ifelse(SexuponOutcome == "Neutered Male" | SexuponOutcome == "Spayed Female", 1 , 0))%>%
        
        # drop the unnecessary column
        select(-c(DateTime, AgeuponOutcome))
}
```
```{r}
# Apply
train_1 <- FeatureExtract(train)
train_1%>%
    select(-c(AnimalID, OutcomeSubtype)) -> train_1
test_1 <- FeatureExtract(test)
```

###(1) BREED_PURE
```{r}
# Breed_Str_Function
Breed_Str_Function <- function(data){
    ifelse(grepl('Mix', data) == TRUE, "Mix",
        ifelse(grepl("/", data) == TRUE,"with", "Pure"))
}
```

```{r}
# apply
train_1$Breed_Pure <- NULL
train_1$Breed_Pure <- sapply(train_1$Breed, FUN = Breed_Str_Function)

test_1$Breed_Pure <- NULL
test_1$Breed_Pure <- sapply(test_1$Breed, FUN = Breed_Str_Function)
```


###(2) COLOR_SIMPLE
```{r}
# Color_Str_Function
Color_Str_Function <- function(data){
    str_split(data, "[/]")[[1]][1]
}
```

```{r}
# apply
train_1$Color_simple <- NULL
train_1$Color_simple <- sapply(train_1$Color, FUN = Color_Str_Function)

test_1$Color_simple <- NULL
test_1$Color_simple <- sapply(test_1$Color, FUN = Color_Str_Function)
```


```{r}
train_1%>%
    group_by(Color)%>%
    summarise(count = n()) %>%
    arrange(desc(count), Color)

train_1%>%
    group_by(Color_simple)%>%
    summarise(count = n()) %>%
    arrange(desc(count), Color_simple)
```



###(3) BREED_SIMPLE
```{r}
i = unique(train_1$AnimalType)[2]
head(train_1$Breed)
for(i in unique(train_1$AnimalType)){
    train_1%>%
        filter(AnimalType == i)%>%
        group_by(Breed)%>%
        summarise(count = n())%>%
        arrange(desc(count)) -> k 

    assign(paste0('train_',as.factor(i),'Breed Count'), k)
}
head(`train_CatBreed Count`)
head(`train_DogBreed Count`)
```
*We could see that there is too much breed speiecs in dog data*

```{r}
# BREED_Str_Function
Breed_Str_Function <- function(data){
    str_split(data, "[/]")[[1]][1]
}
```

```{r}
# apply
train_1$Breed_simple <- NULL
train_1$Breed_simple <- sapply(train_1$Breed, FUN = Breed_Str_Function)

test_1$Breed_simple <- NULL
test_1$Breed_simple <- sapply(test_1$Breed, FUN = Breed_Str_Function)
```

```{r}
#result
length(unique(train$Breed))  # before simplify
length(unique(train_1$Breed_simple)) # after simplify
```


##3) LIST WISE DELETION
```{r}
# train
nrow(train_1) # 26,729 row, before to list wise deletion
nrow(train_1[complete.cases(train_1),]) # 26728 row, after list wise deletion 
train_1[complete.cases(train_1) == FALSE,]
# train_1 <- train_1[complete.cases(train_1) == TRUE,] # if i could know the relation btwn AGE and Sex as Animaltype, i could guess this NA also.  
                                                       # So i'm gonna do this next paragraph

# test
nrow(test_1)
nrow(test_1[complete.cases(test_1) == FALSE,]) # there is no more NA in test data
```

###1) RELATIONSHIP BTWN AGE, SEX AS ANIMALTYPE
```{r}
train%>%
    filter(is.na(SexuponOutcome) == FALSE,
           AnimalType == "Dog",
           Breed == "Dachshund",
           OutcomeType == "Return_to_owner") %>%
    ggplot(aes(x = SexuponOutcome , y = AGE, fill = SexuponOutcome)) +
    geom_boxplot() +
    geom_point() 
```
*Through above graph, this one's Sex might be "Neutered Male"*

###2) INTERPOLATE SexuponOutcome's NA 
```{r}
# Interpolation
train_1[!complete.cases(train_1),"SexuponOutcome"]  <- "Neutered Male"
train_1[!complete.cases(train_1),"Sex_Dummy"]  <- 1
# check
train_1[complete.cases(train_1) == FALSE,] # now, there is no more NA !
```



#3. VISUALIZAION
##1) OUTCOME
###(1) AS NAME EXISTENCE
```{r}
train_1%>%
    group_by(Name, OutcomeType)%>%
    summarise(count = n()) %>%
    arrange(OutcomeType) %>% 
    ggplot(aes(x = reorder(OutcomeType, count), y = count, fill = Name)) +
    geom_col(position = "dodge")

train_1%>%
    mutate(OutcomeType_2 = ifelse(OutcomeType == "Died" | OutcomeType == "Euthanasia", "Bad", "Good")) %>%
    group_by(Name, OutcomeType, OutcomeType_2)%>%
    summarise(count = n()) %>%
    arrange(OutcomeType) %>% 
    ggplot(aes(x = reorder(OutcomeType_2, count), y = count, fill = Name)) +
    geom_col(position = "dodge")
```
*we could see that if animal has name, her pct of transfer or return to owener is increased.*

###(2) AS SEX
```{r}
table((train_1$SexuponOutcome))
```

```{r}
for(i in 1:length(unique(train_1$SexuponOutcome))){
train_1%>%
    filter(SexuponOutcome == unique(train_1$SexuponOutcome)[i])%>%
    group_by(OutcomeType)%>%
    summarise(count = n()) %>%
    ggplot(aes(x = OutcomeType, y = count,  fill = OutcomeType)) +
    geom_col(position = "dodge") +
    ggtitle(unique(train_1$SexuponOutcome)[i]) +
    geom_text(aes(label = count)) +
    theme(legend.position="none", 
          axis.text.x = element_text(angle = 90, face = "italic", vjust = 1 ,hjust = 1),
          plot.title = element_text(face = "bold.italic", hjust = 0.5)) -> k
   
     assign(paste0("VIS_",i), k)
}
```

```{r}
library(gridExtra)
grid.arrange(VIS_1,VIS_2, ncol = 2) # neutralization
grid.arrange(VIS_3,VIS_4, ncol = 2) # not neutralization
VIS_5 # i think, unknown also has some meaning.
```
*i've made a dummy variable of sexuponoutcome*

###(3) AS CAT OR DOG
```{r}
train_1%>%
    group_by(OutcomeType, AnimalType)%>%
    summarise(count = n())%>%
    ggplot(aes(x = OutcomeType, y = count , fill = AnimalType)) +
    geom_col(position = "dodge") +
    geom_text(aes(label = count), position = position_dodge(width = 1)) # using position dodge and width, i could make text on each col
```


###(4) AS BREED
 :finding whether purebred or not
```{r}
train_1%>%
    group_by(OutcomeType, Breed_Pure) %>%
    summarise(count = n()) %>%
    group_by(Breed_Pure) %>%
    mutate(count_sum = sum(count),
           ratio = count / count_sum) %>%
    ggplot(aes(x = OutcomeType, y = ratio, fill = factor(Breed_Pure))) +
    geom_col(position = "dodge") +
    geom_text(aes(label = round(ratio,digits = 2)), stat = ,position = position_dodge(width = 1))
```
*sample count btwn mix and pure is too difference => So i use the each ratio value*


###(5) AS COLOR
```{r}
# original color 
for(i in 1:length(unique(train_1$OutcomeType))){
    train_1%>%
    filter(OutcomeType == unique(OutcomeType)[i]) %>%
    group_by(Color)%>%
    summarise(count = n()) %>%
    ggplot(aes(x = Color, y = count, fill = Color)) +
    geom_col() +
    ggtitle(unique(train_1$OutcomeType)[i]) +
    theme(legend.position="none", 
          axis.text.x = element_text(angle = 90, face = "italic", vjust = 1 ,hjust = 1),
          plot.title = element_text(face = "bold.italic", hjust = 0.5)) -> k
    print(k)
}
```

```{r}
# simple color
for(i in 1:length(unique(train_1$OutcomeType))){
    train_1%>%
    filter(OutcomeType == unique(OutcomeType)[i]) %>%
    group_by(Color_simple)%>%
    summarise(count = n()) %>%
    ggplot(aes(x = Color_simple, y = count, fill = Color_simple)) +
    geom_col() +
    ggtitle(unique(train_1$OutcomeType)[i]) +
    theme(legend.position="none", 
          axis.text.x = element_text(angle = 90, face = "italic", vjust = 1 ,hjust = 1),
          plot.title = element_text(face = "bold.italic", hjust = 0.5)) -> k
    print(k)
}
```

#4. DIVIDING CAT & DOG
```{r}

```



#5. MODELING
##1) ONE HOT ENCODING
```{r}
# data
train_1
#train_shelter_mat <- model.matrix(OutcomeType ~ +. , train_1)
```






























