---
layout : post
title: "Shiny_study_6"
subtitle: "Use reactive expressions"
author: "ooDoo"
date: 2018-03-20
categories : study
cover : /assets/article_images/title/instacode_sizedown.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
# install.packages(c("maps", "mapproj")) # helpers.R uses the maps and mapproj packages in R


# set the working directory 
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/10. Shiny/ShinyStudy")
```

# 1. To get started
```{r}
#install.packages("quantmod")
library(quantmod)
runApp("stockVis")
```


•Create a new folder named stockVis in your working directory.
•Download the following files and place them inside stockVis: app.R and helpers.R.
•Launch the app with runApp("stockVis")


# 2. stockVis relies on two functions(from the quantmod package)

## 1) `usesgetSymbols` 
: to download financial data straight into R from websites like Google finance and the Federal Reserve Bank of St. Louis.

## 2) `chartSeries` 
: to display prices in an attractive chart.


# 3. Check boxes and date ranges
## 1) `dateRangeInput`
 : date range selector
 
## 2) `checkboxInput`
 : a couple of check boxes, Check boxes return a TRUE when the check box is checked, and a FALSE when the check box is not checked.

The check boxes are named `log` and `adjust` in the `ui` object, which means you can look them up as `input$log` and `input$adjust` in the server function. If you’d like to review how to use widgets and their values, check out Lesson 3 and Lesson 4.


# 4. Streamline computation
```{r}
output$plot <- renderPlot({
  data <- getSymbols(input$symb, src = "google",
                     from = input$dates[1],
                     to = input$dates[2],
                     auto.assign = FALSE)

  chartSeries(data, theme = chartTheme("white"),
              type = "line", log.scale = input$log, TA = NULL)
})
```

- it re-fetches the data from Google finance with getSymbols, and
- it re-draws the chart with the correct axis.


# 5. Reactive expressions
You can limit what gets re-run during a reaction with reactive expressions.

A reactive expression is an R expression that uses widget input and returns a value. The reactive expression will update this value whenever the original widget changes.

To create a reactive expression use the `reactive` function, which takes an R expression surrounded by braces (just like the `render*` functions).

For example, here’s a reactive expression that uses the widgets of stockVis to fetch data from Google.
```{r}
dataInput <- reactive({
  getSymbols(input$symb, src = "google",
    from = input$dates[1],
    to = input$dates[2],
    auto.assign = FALSE)
})
```

```{r}
output$plot <- renderPlot({    
  chartSeries(dataInput(), theme = chartTheme("white"),
    type = "line", log.scale = input$log, TA = NULL)
})
```



# ※ summarize reactive expression
•A reactive expression saves its result the first time you run it.

•The next time the reactive expression is called, it checks if the saved value has become out of date (i.e., whether the widgets it depends on have changed).

•If the value is out of date, the reactive object will recalculate it (and then save the new result).

•If the value is up-to-date, the reactive expression will return the saved value without doing any computation.

=> to prevent Shiny from re-running code unnecessarily
    

*Consider how a reactive expression will work in the new stockVis app below.*
```{r}
server <- function(input, output) {

  dataInput <- reactive({
    getSymbols(input$symb, src = "google",
               from = input$dates[1],
               to = input$dates[2],
               auto.assign = FALSE)
  })

  output$plot <- renderPlot({

    chartSeries(dataInput(), theme = chartTheme("white"),
                type = "line", log.scale = input$log, TA = NULL)
  })

}
```
When you click “Plot y axis on the log scale”, input$log will change and renderPlot will re-execute. Now
1.renderPlot will call dataInput()
2.dataInput will check that the dates and symb widgets have not changed
3.dataInput will return its saved data set of stock prices without re-fetching data from Google
4.renderPlot will re-draw the chart with the correct axis


# 6. Dependencies
What if your user changes the stock symbol in the symb widget?

This will make the plot drawn by renderPlot out of date, but renderPlot no longer calls `input$symb`. Will Shiny know that `input$symb` has made plot out of date?

Yes, Shiny will know and will redraw the plot. Shiny keeps track of which reactive expressions an output object depends on, as well as which widget inputs. Shiny will automatically re-build an object if
•an input value in the objects’s render* function changes, or
•a reactive expression in the objects’s render* function becomes obsolete

Think of reactive expressions as links in a chain that connect input values to output objects. The objects in output will respond to changes made anywhere downstream in the chain. (You can fashion a long chain because reactive expressions can call other reactive expressions.)

Only call a reactive expression from within a reactive or a render*function. Why? Only these R functions are equipped to deal with reactive output, which can change without warning. In fact, Shiny will prevent you from calling reactive expressions outside of these functions.


# 7. Warm up
Time to fix the broken check box for “Adjust prices for inflation.” Your user should be able to toggle between prices adjusted for inflation and prices that have not been adjusted.
Here’s one solution below, but it is not ideal. Can you spot why? Once again it has to do with input$log.
```{r}
server <- function(input, output) {

  dataInput <- reactive({
    getSymbols(input$symb, src = "google",
        from = input$dates[1],
        to = input$dates[2],
        auto.assign = FALSE)
  })

  output$plot <- renderPlot({   
    data <- dataInput()
    if (input$adjust) data <- adjust(dataInput())

    chartSeries(data, theme = chartTheme("white"),
        type = "line", log.scale = input$log, TA = NULL)
  })
}
```
adjust is called inside renderPlot. If the adjust box is checked, the app will readjust all of the prices each time you switch from a normal y scale to a logged y scale. This readjustment is unnecessary work.

▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼▼
Now you have isolated each input in its own reactive expression or render* function. If an input changes, only out of date expressions will re-run.
```{r}
server <- function(input, output) {

  dataInput <- reactive({  
      getSymbols(input$symb, src = "google",
          from = input$dates[1],
          to = input$dates[2],
          auto.assign = FALSE)
  })

  finalInput <- reactive({
    if (!input$adjust) return(dataInput())
    adjust(dataInput())
  })

  output$plot <- renderPlot({
    chartSeries(finalInput(), theme = chartTheme("white"),
        type = "line", log.scale = input$log, TA = NULL)
  })
}
```

Here’s an example of the flow:
•A user clicks “Plot y axis on the log scale.”
•`renderPlot` re-runs.
•`renderPlot` calls `finalInput`.
•`finalInput` checks with `dataInput` and `input$adjust`.
•If neither has changed, `finalInput` returns its saved value.
•If either has changed, `finalInput` calculates a new value with the current inputs. It will pass the new value to `renderPlot` and store the new value for future queries.


# 8. Recap

You can make your apps faster by modularizing your code with reactive expressions.

•A reactive expression takes input values, or values from other reactive expressions, and returns a new value
•Reactive expressions save their results, and will only re-calculate if their input has changed
•Create reactive expressions with reactive({ })
•Call reactive expressions with the name of the expression followed by parentheses ()
•Only call reactive expressions from within other reactive expressions or render* functions

You can now create sophisticated, streamlined Shiny apps. The final lesson in this tutorial will show you how to share your apps with others.






