---
layout : post
title: "Shiny_study_2"
subtitle: "build your first app from scratch."
author: "ooDoo"
date: 2018-03-09
categories : study
cover : /assets/article_images/title/instacode_sizedown.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Layout

This lesson will show you how to build a user interface for your app. You will learn how to lay out the user interface and then add text, images, and other HTML elements to your Shiny app.

```{r}
library(shiny)

# Define UI ----
ui <- fluidPage(
  
)

# Define server logic ----
server <- function(input, output) {
  
}

# Run the app ----
shinyApp(ui = ui, server = server)
```
This code is the bare minimum needed to create a Shiny app


# 2. fluidPage
: make titlePanel and side barLayout

```{r}
ui <- fluidPage(
  titlePanel("title panel"),

  sidebarLayout(
    sidebarPanel("sidebar panel"),
    mainPanel("main panel")
  )
)
```

## 1) sidebarLayout's two arguments
• `sidebarPanel` : function output
• `mainPanel` : function output

```{r}
ui <- fluidPage(
  titlePanel("title panel"),
  
  sidebarLayout(position = "right",
                sidebarPanel("sidebar panel"),
                mainPanel("main panel")
  )
)
```

titlePanel and sidebarLayout create a basic layout for your Shiny app, but you can also create more advanced layouts. You can use navbarPage to give your app a multi-page user interface that includes a navigation bar. Or you can use fluidRow and column to build your layout up from a grid system. If you’d like to learn more about these advanced options, read the ![Shiny Application Layout Guide](https://shiny.rstudio.com/articles/layout-guide.html). We will stick with sidebarLayout in this tutorial.


# 3. HTML content

shiny function HTML5 equivalent creates

p <p> A paragraph of text 
h1 <h1> A first level header 
h2 <h2> A second level header 
h3 <h3> A third level header 
h4 <h4> A fourth level header 
h5 <h5> A fifth level header 
h6 <h6> A sixth level header 
a <a> A hyper link 
br <br> A line break (e.g. a blank line) 
div <div> A division of text with a uniform style 
span <span> An in-line division of text with a uniform style 
pre <pre> Text ‘as is’ in a fixed width font 
code <code> A formatted block of code 
img <img> An image 
strong <strong> Bold text 
em <em> Italicized text 
HTML   Directly passes a character string as HTML code 


# 4. Headers
```{r}
ui <- fluidPage(
  titlePanel("My Star Wars App"),
  sidebarLayout(
    sidebarPanel(),
    mainPanel(
      h6("Episode IV", align = "center"),
      h6("A NEW HOPE", align = "center"),
      h5("It is a period of civil war.", align = "center"),
      h4("Rebel spaceships, striking", align = "center"),
      h3("from a hidden base, have won", align = "center"),
      h2("their first victory against the", align = "center"),
      h1("evil Galactic Empire.")
    )
  )
)
```


# 5. Formatted text
```{r}
ui <- fluidPage(
  titlePanel("My Shiny App"),
  sidebarLayout(
    sidebarPanel(),
    mainPanel(
      p("p creates a paragraph of text."),
      p("A new p() command starts a new paragraph. Supply a style attribute to change the format of the entire paragraph.", style = "font-family: 'times'; font-si16pt"),
      strong("strong() makes bold text."),
      em("em() creates italicized (i.e, emphasized) text."),
      br(),
      code("code displays your text similar to computer code"),
      div("div creates segments of text with a similar style. This division of text is all blue because I passed the argument 'style = color:blue' to div", style = "color:blue"),
      br(),
      p("span does the same thing as div, but it works with",
        span("groups of words", style = "color:blue"),
        "that appear inside a paragraph.")
    )
  )
)
```


# 6. Images
```{r}
img(src = "my_image.png", height = 72, width = 72)
```
The img function looks for your image file in a specific place. Your file must be in a folder named `www` in the same directory as the app.R script. Shiny treats this directory in a special way. Shiny will share any file placed here with your user’s web browser, which makes `www` a great place to put images, style sheets, and other things the browser will need to build the wep components of your Shiny app.

```{r}
ui <- fluidPage(
  titlePanel("My Shiny App"),
  sidebarLayout(
    sidebarPanel(),
    mainPanel(
      img(src = "rstudio.png", height = 140, width = 400)
    )
  )
)
```


# 7. Test 
```{r}
library(shiny)

# Define UI ----
ui <- fluidPage(
  titlePanel("My Shiny App"),
  sidebarLayout(
    sidebarPanel(
      h2("Installation"),
      p("Shiny is available on CRAN, so you can install it in the usual way from your R console:"),
      code('install.packages("shiny")'),
      br(),
      br(),
      br(),
      br(),
      img(src = "rstudio.png", height = 70, width = 200),
      br(),
      "Shiny is a product of ", 
      span("RStudio", style = "color:blue")
    ),
    mainPanel(
      h1("Introducing Shiny"),
      p("Shiny is a new package from RStudio that makes it ", 
        em("incredibly easy "), 
        "to build interactive web applications with R."),
      br(),
      p("For an introduction and live examples, visit the ",
        a("Shiny homepage.", 
          href = "http://shiny.rstudio.com")),
      br(),
      h2("Features"),
      p("- Build useful web applications with only a few lines of code—no JavaScript required."),
      p("- Shiny applications are automatically 'live' in the same way that ", 
        strong("spreadsheets"),
        " are live. Outputs change instantly as users modify inputs, without requiring a reload of the browser.")
    )
  )
)

# Define server logic ----
server <- function(input, output) {
  
}

# Run the app ----
shinyApp(ui = ui, server = server)
```


