---
layout : post
title: "Shiny_study_3"
subtitle: "Add control widgets "
author: "ooDoo"
date: 2018-03-11
categories : study
cover : /assets/article_images/title/instacode_sizedown.png
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 1. Control widgets
: This lesson will show you how to build a user interface for your app. You will learn how to lay out the user interface and then add text, images, and other HTML elements to your Shiny app. 

## 1) The standard Shiny widgets 

함수명|기능
:---:|:---:
`actionButton` | Action Button 
`checkboxGroupInput` | A group of check boxes 
`checkboxInput` | A single check box 
`dateInput` | A calendar to aid date selection 
`dateRangeInput` | A pair of calendars for selecting a date range 
`fileInput` | A file upload control wizard 
`helpText` | Help text that can be added to an input form 
`numericInput` | A field to enter numbers 
`radioButtons` | A set of radio buttons 
`selectInput` | A box with choices to select from 
`sliderInput` | A slider bar 
`submitButton` | A submit button 
`textInput` | A field to enter text 


# 2. Adding widgets

## 1) arguments
The first two arguments

•a name for the widget: 결과물에 노출되지는 않지만, 추후 위젯 정보에 접근하는데 사용되며, 반드시 string으로 입력해야됨
•a label: 결과물에 노출 되는 이름으로, 역시 반드시 string으로 작성해야 하며 공란(" ")으로 남겨두어도 가능하다.     
```{r}
# Exampe
#actionButton("action", # a name for the widget 
#              "Action") # a label
```

*위젯 별로 다양한 arguments가 필요하며, 각각의 필요한  arguments는 function's help page를 통해서 알 수 있다.*
ex.) `?selectInput`

```{r}
library(shiny)

# Define UI ----
ui <- fluidPage(
  titlePanel("Basic widgets"),
  
  fluidRow(
    
    column(3,
           h3("Buttons"),
           actionButton("action", # a name for the widget 
                        "Action"), # a label
           br(),
           br(), 
           submitButton("Submit")),
    
    column(3,
           h3("Single checkbox"),
           checkboxInput("checkbox", "Choice A", value = TRUE)),
    
    column(3, 
           checkboxGroupInput("checkGroup", 
                              h3("Checkbox group"), 
                              choices = list("Choice 1" = 1, 
                                             "Choice 2" = 2, 
                                             "Choice 3" = 3), # using list for many select
                              selected = 1)),
    
    column(3, 
           dateInput("date",  # a name for the widget
                     h3("Date input"), 
                     value = "2014-01-01"))   
  ),
  
  fluidRow(
    
    column(3,
           dateRangeInput("dates",
                          h3("Date range"))),
    
    column(3,
           fileInput("file",
                     h3("File input"))),
    
    column(3, 
           h3("Help text"),
           helpText("Note: help text isn't a true widget,", 
                    "but it provides an easy way to add text to",
                    "accompany other widgets.")),
    
    column(3, 
           numericInput("num", 
                        h3("Numeric input"), 
                        value = 1)) # set the default value   
  ),
  
  fluidRow(
    
    column(3,
           radioButtons("radio", h3("Radio buttons"),
                        choices = list("Choice 1" = 1, "Choice 2" = 2,
                                       "Choice 3" = 3),selected = 1)),
    
    column(3,
           selectInput("select", h3("Select box"), 
                       choices = list("Choice 1" = 1, "Choice 2" = 2,
                                      "Choice 3" = 3), selected = 1)),
    
    column(3, 
           sliderInput("slider1", h3("Sliders"),
                       min = 0, max = 100, value = 50),
           sliderInput("slider2", "",
                       min = 0, max = 100, value = c(25, 75))
    ),
    
    column(3, 
           textInput("text", h3("Text input"), 
                     value = "Enter text..."))   
  )
  
)

# Define server logic ----
server <- function(input, output) {
  
}

# Run the app ----
shinyApp(ui = ui, server = server)
```

# 3. Practice 
```{r}
library(shiny)

# Define UI ----
ui <- fluidPage(
  titlePanel("censusVis"),

  sidebarPanel(
      helpText("Creat demographic maps with information from the 2010 US Census."),
       br(),
       selectInput(inputId = "select",
                   label = strong("Choose a variable to display"), 
                   choices = list("percent White", 
                                  "Percent Black", 
                                  "Percent Hispanic",
                                  "Percent Asian"),
                                  selected = "Percent White"),
       br(),
       sliderInput(inputId = "slider_1",
                   label = strong("Range of interest"),
                   min = 0, max = 100,
                   value =c(30, max)) # value : initial value
        ) 
)

# Define server logic ----
server <- function(input, output) {
  
}

# Run the app ----
shinyApp(ui = ui, server = server)
```

# 4. Shiny Widgets Gallery
![Shiny Widgets Gallery](http://shiny.rstudio.com/gallery/widget-gallery.html)

# 5. Recap
It is easy to add fully functional widgets to your Shiny app.
•Shiny provides a family of functions to create these widgets.

•Each function requires a name and a label.

•Some widgets need specific instructions to do their jobs.

•You add widgets to your Shiny app just like you added other types of HTML content (see Lesson 2)









