---
layout : post
title: "Shiny_study_7"
subtitle: "Share your apps"
author: "ooDoo"
date: 2018-03-21
categories : study
cover : /assets/article_images/title/instacode_sizedown.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
# install.packages(c("maps", "mapproj")) # helpers.R uses the maps and mapproj packages in R


# set the working directory 
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/10. Shiny/ShinyStudy")
```


# 1. Two basic options to sharing Shiny apps

## 1) Share your Shiny app as R scripts.
: This is the simplest way to share an app, but it works only if your users have R on their own computer (and know how to use it). Users can use these scripts to launch the app from their own R session, just like you’ve been launching the apps so far in this tutorial.


## 2) Share your Shiny app as a web page.
: This is definitely the most user friendly way to share a Shiny app. Your users can navigate to your app through the internet with a web browser. They will find your app fully rendered, up to date, and ready to go.


# 2. Share as R scripts
 : Anyone with R can run your Shiny app. They will need a copy of your app.R file, as well as any supplementary materials used in your app (e.g., www folders or helpers.R files).

# 3. Hosted online
 : Shiny has three built in commands that make it easy to use files that are hoseted online 

## 1) `runUrl`
 : `runUrl` will download and launch a shiny app straight from a weblink

*To use* `runURL`
 • Save your Shiny app’s directory as a zip file
 • Host that zip file at its own link on a web page. Anyone with access to the link can launch the app from inside R by running
```{r}
library(shiny)
runUrl( "<the weblink>")
```
  
  
## 2) `runGitHub`
 : If you don’t have your own web page to host the files at, you can host your the files for free at www.github.com. 
 
*To use* `runGitHub`
 • create a project repository on GitHub. 
 • Then store your app.R file in the repository, along with any supplementary files that the app uses.
 
Your users can launch your app by running:
```{r}
runGitHub( "<your repository name>", "<your user name>") 
```


## 3) `runGist`
If you want an anonymous way to post files online, GitHub offers a pasteboard service for sharing files at gist.github.com

*To use* `runGitHub`
 • Copy and paste your `app.R` files to the gist web page.
 • Note the URL that GitHub gives the gist
 
 Once you’ve made a gist, your users can launch the app with runGist("<gist number>") where "<gist number>" is the number that appears at the end of your Gist’s web address
 
  ![Here](https://gist.github.com/mine-cetinkaya-rundel/eb3470beb1c0252bd0289cbc89bcf36f) is an example of an app hosted as a gist. You could launch this app with:
```{r}
runGist("eb3470beb1c0252bd0289cbc89bcf36f")
```

*★ All of the above methods share the same limitation. They require your user to have R and Shiny installed on their computer.★*

# 4. Share as a web page
 : to share output with people who do not have R (and have no intention of getting it). 
 
*RStudio offers four ways to host your Shiny app as a web page *
 1) shinyapps.io
 2) Shiny Server
 3) Shiny Server Pro
 4) RStudio Connect

## 1) Shinyapps.io
 : The easiest way to turn your Shiny app into a web page is to use shinyapps.io, RStudio’s hosting service for Shiny apps.
 
shinyapps.io lets you upload your app straight from your R session to a server hosted by RStudio. You have complete control over your app including server administration tools. You can find out more about shinyapps.io by visiting http://www.shinyapps.io/
 
 
## 2) Shiny Server
 : builds a web server designed to host Shiny apps. It’s free, open source, and available from GitHub.
 
 Shiny Server is a server program that Linux servers can run to host a Shiny app as a web page. To use Shiny Server, you’ll need a Linux server that has explicit support for Ubuntu 12.04 or greater (64 bit) and CentOS/RHEL 5 (64 bit). *If you are not using an explicitly supported distribution, you can still use Shiny Server by building it from source.*

You can host multiple Shiny applications on multiple web pages with the same Shiny Server, and you can deploy the apps from behind a firewall.

To see detailed instructions for installing and configuring a Shiny Server, visit the Shiny Server ![Guide](https://github.com/rstudio/shiny-server/blob/master/README.md)

 
## 3) Shiny Server Pro
Shiny Server will get your app to the web and take care of all of your Shiny publishing needs. However, if you use Shiny in a for-profit setting, you may want to give yourself the server tools that come with most paid server programs, such as
•Password authentification
•SSL support
•Administrator tools
•Priority support
•and more.

If so, check out Shiny Server Pro, RStudio’s paid professional version of Shiny Server.



## 4) RStudio Connect
: RStudio Connect is a new publishing platform for the work your teams create in R. Share Shiny applications, R Markdown reports, Plumber APIs, dashboards, plots, and more in one convenient place. Use push-button publishing from the RStudio IDE, scheduled execution of reports, and flexible security policies to bring the power of data science to your entire enterprise.
![RStudio Connect](https://www.rstudio.com/products/connect/)


# 5. Recap
Shiny apps are easy to share. You can share your app as a couple of R scripts, or as a fully functioning web app with its own URL. Each method has its own advantages.

You learned:
•Anyone can launch your app as long as they have a copy of R, Shiny, and a copy of your app’s files.
•runUrl, runGitHub, and runGist make it simple to share and retrieve Shiny files from web links.
•You can turn your app into a live web app at its own URL with shinyapps.io.
•You can use the open source Shiny Server to build a Linux server that hosts Shiny apps.
•If you need closer control, or want to manage large volumes of traffic, you can purchase Shiny Server Pro or RStudio Connect from RStudio.

 
 
 
 
 
 
 
 
 
 
 


