---
layout : post
title: "Shiny_study_5"
subtitle: "Use R scripts and data "
author: "ooDoo"
date: 2018-03-18
categories : study
cover : /assets/article_images/title/instacode_sizedown.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
# install.packages(c("maps", "mapproj")) # helpers.R uses the maps and mapproj packages in R


# set the working directory 
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/10. Shiny/ShinyStudy")
```

# 1. roads the data
```{r}
counties <- readRDS("counties.rds")
head(counties)
```


# 2. helpers.r
: R script that can help you make choropleth maps(단계 구분도)
 ※ *A choropleth map : a map that uses color to display the regional variation of a variable*

## 1) 5 argumnets of `percent_map` funtion in helpers.R
Argument|Input
:---:|:---:
`var` | a column vector from the counties.rds dataset 
`color` | any character string you see in the output of colors() 
`legend.title` | A character string to use as the title of the plot’s legend 
`max` | A parameter for controlling shade range (defaults to 100) 
`min` | A parameter for controlling shade range (defaults to 0) 

## 2) plots the counties data as a choropleth map *using helpers.R*
```{r}
library(maps) 
library(mapproj)
source("helpers.R")
counties <- readRDS("counties.rds")
percent_map(var = counties$white,
            color = "royalblue",
            legend.title =  "% White")
```

# 3. Loading files and file paths
위에서 `source` 함수와 `readRDS`함수는 파일 경로를 필요로 한다.(나는 wd를 설정해주었기에 이를 따로 명시하지 않았다.) 
하지만, shiny를 작동하는데 있어서 `server.R`을 지정해놓은 파일이 곧 해당 shiny app의 Working Directory가 될 것이기에 같은 파일안에 데이터와 source파일을 위치시키자.


# 4. Execution
: shiny는 모든 당신의 app.R 스크립트에 위치한 모든 commands를 한꺼번에 실행한다. 하지만, 당신이 해당 commands를 어디에 위치시키는지에 따라 해당 commands가 몇번 실행되는지는 다르게 결정되는데, 이는 당신의 app의 성능에 영향을 미치게 된다. 그 이유는 shiny는 당신의app.R script의 특정 section을 다른 section보다 더 자주 실행하기 때문이다.

Shiny saves the server function until a new user arrives. Each time a new user visits your app, Shiny runs the server function again, one time. The function helps Shiny build a distinct set of reactive objects for each user.

As users interact with the widgets and change their values, Shiny will re-run the R expressions assigned to each reactive object that depend on a widget whose value was changed. If your user is very active, these expressions may be re-run many, many times a second.

[요약]
• `shinyApp function`은 app을 설치할 때 한번 실행
• `server funciton`은 매번app을 방문할 때마다 한번씩 실행됨
• `render*`함수 안에 있는 `R expressions`은 유저가 widget의 값을 변경할 때마다 실행됨


# 5. Tip to placing the funtion right place using above information 
## 1) `server function` 외부 : Source scripts, load libraries, and read data sets

## 2) `server function` 내부(utside of any render* calls) : 사용자의 specific objects

## 3) inside of a `render*` : place code that Shiny must rerun to build an object
: *Shiny will rerun all of the code in a "render" chunk each time a user changes a widget mentioned in the chunk* 


# 6. Practice
## 1) 1st Step
```{r}
# basic setting to build active map using "helpers.R"
source("helpers.R") # Source helper functions
counties <- readRDS("counties.rds") # Load data 

library(maps)
library(mapproj)

# build app
# User interface ----
 ui <- fluidPage(
  titlePanel("censusVis"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Create demographic maps with 
        information from the 2010 US Census."),
      
      selectInput(inputId = "var", 
                  label = "Choose a variable to display",
                  choices = c("Percent White", "Percent Black",
                              "Percent Hispanic", "Percent Asian"),
                  selected = "Percent White"),
      
      sliderInput(inputId = "range", 
                  label = "Range of interest:",
                  min = 0, max = 100, value = c(0, 100))
    ),
    
    mainPanel(plotOutput("map")) # setting the place of map
    )
)

# Server logic ----
server <- function(input, output) {
  output$map <- renderPlot({
    percent_map(var = counties$white,
                color = "plum2",
                legend.title = "census")
  })
}

# Run app ----
shinyApp(ui, server)
```


## 2) 2nd Step
```{r}
# basic setting to build active map using "helpers.R"
source("helpers.R") # Source helper functions
counties <- readRDS("counties.rds") # Load data 

library(maps)
library(mapproj)

# build app
# User interface ----
 ui <- fluidPage(
  titlePanel("censusVis"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Create demographic maps with 
        information from the 2010 US Census."),
      
      selectInput(inputId = "var", 
                  label = "Choose a variable to display",
                  choices = c("Percent White", "Percent Black",
                              "Percent Hispanic", "Percent Asian"),
                  selected = "Percent White"),
      
      sliderInput(inputId = "range", 
                  label = "Range of interest:",
                  min = 0, max = 100, value = c(0, 100))
    ),
    
    mainPanel(plotOutput("map")) # setting the place of map
    )
)

# Server logic ----
server <- function(input, output) {
  output$map <- renderPlot({
    data <- switch(input$var,    # switch the data 
                   "Percent White" = counties$white,
                   "Percent Black" = counties$black,
                   "Percent Hispanic" = counties$hispanic,
                   "Percent Asian" = counties$asian)
    
    color <- switch(input$var,   # switch the color
                    "Percent White" = "darkgreen",
                    "Percent Black" = "black",
                    "Percent Hispanic" = "darkorange",
                    "Percent Asian" = "darkviolet")
    
    legend <- switch(input$var,  # switch the legend
                     "Percent White" = "% White",
                     "Percent Black" = "% Black",
                     "Percent Hispanic" = "% Hispanic",
                     "Percent Asian" = "% Asian")
    
    percent_map(var = data,
                color = color,
                legend.title = legend,
                min = input$range[1], 
                max = input$range[2])
  })
}

# Run app ----
shinyApp(ui, server)
```


# 7. Recap

Keep in mind:
•The directory that app. R appears in will become the working directory of the Shiny app

•Shiny will run code placed at the start of app.R, before the server function, only once during the life of the app.

•Shiny will run code placed inside server function multiple times, which can slow down the app.