---
layout : post
title: "ggvis_study"
author: "ooDoo"
date: 2018-04-04
categories : ggvis
cover : /assets/article_images/title/instacode_sizedown.png
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# basic package
library(ggplot2)
library(ggthemr)
library(dplyr)
library(data.table)
library(readr)
library(ggvis)
library(knitr)


# install the latest development version 
# install.packages("devtools")
#devtools::install_github("hadley/lazyeval", build_vignettes = FALSE)
#devtools::install_github("hadley/dplyr", build_vignettes = FALSE)
#devtools::install_github("rstudio/ggvis", build_vignettes = FALSE)

#setwd
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/12. ggvis")
```

# 1. Dive into plotting with `ggvis`

## 1) basic Usage
```{r}
layer_points(ggvis(mtcars, x = ~wt, y = ~mpg))
```

```{r}
head(mtcars)
```


## 2) Using `dplyr`
```{r}
library(dplyr)
mtcars %>%
    mutate(disp = disp / 61.0237) %>% # convert engine displacment to litres
    ggvis(x = ~mpg, y = ~disp) %>%
    layer_points() %>%
    set_options(width = 300, height = 200,
                padding = padding(10, 10, 10, 10)) -> x

view_dynamic(x, port = NULL, quiet = FALSE)
```
*변수 앞에 "~"를 붙이는 이유*
 : ggvis안에서 사용하려는 변수는 실제 벡터 혙태로 저장 되어있는 변수가 아닌, 해당 데이터셋에서만 존재하는 컬럼이기에 이를 구분해 주기 위해서 반드시 "~"를 앞에 붙여야 한다. 
 
## 3) Mapping tools
 - `fill`
 - `stroke` 
 - `size`
 - `shape`
 
### (1) fill 
```{r}
# factors
mtcars %>% 
    ggvis(~mpg, ~disp, fill = ~as.factor(vs)) %>% 
    layer_points()

# numeric
mtcars %>% 
    ggvis(~mpg, ~disp, fill = ~qsec) %>% 
    layer_points()

# fixed colour
mtcars %>% 
    ggvis(~mpg, ~disp, fill := "skyblue") %>% 
    layer_points()
```
: same as ggplot's usage, but If you want to make the points a fixed colour or size, you need to use `:=` instead of `=`. 
 
### (2) stroke 
```{r}
# setting the stroke color using varialbe
mtcars %>%
    ggvis(~mpg, ~disp, stroke = ~vs) %>%
    layer_points()

# setting the stroke color using the fixed colour 
mtcars %>%
    ggvis(~mpg, ~disp, stroke := "black") %>%
    layer_points()
```
 
### (3) size
```{r}
mtcars %>%
    ggvis(~mpg, ~disp, size = ~vs) %>% 
    layer_points()
```
 

### (4) shape
```{r}
# shape  
mtcars %>% 
    ggvis(~mpg, ~disp, shape := "diamond") %>%
    layer_points() 

# shape differently as variable
mtcars %>% 
    ggvis(~mpg, ~disp, shape = ~factor(cyl)) %>%
    layer_points() 

# shape and color
mtcars %>% 
    ggvis(~mpg, ~disp, shape = ~factor(cyl), fill = ~as.factor(cyl)) %>%
    layer_points() 
```
*i don't know how to readjust the legend in ggvis yet*

 
### (5) opacity(alpha value in ggplot)
```{r}
mtcars %>% 
    ggvis(~wt, ~mpg, size := 300, opacity := 0.4) %>%
    layer_points()
```
 
 
#2. Interaction_using mouse
## (1) input_slider() 
### (1) control the size and opacity 
```{r}
mtcars %>% 
  ggvis(~wt, ~mpg, 
    size := input_slider(10, 100),
    opacity := input_slider(0, 1)) %>% 
  layer_points()
```

*the result gonna show on the *Viewer of Rstudio
if we want pass the next step, we have to quit the result such as shiny-apps

### (2) width and centers of histogram bins
```{r}
mtcars %>% 
    ggvis(~wt) %>% # since histogram only takes list of data type, indexing the value as above using "~""
    layer_histograms(width = input_slider(0, 4, step = 0.10, label = "width"),
                     center = input_slider(0, 2, step = 0.05, label = "center"))
```


## (2) input_checkbox
```{r}
    
```




#2. Interaction_using keyboard
```{r}
keys_s <- left_right(10, 1000, step = 50)
mtcars %>%
    ggvis(~wt, ~mpg, size := keys_s, opacity := 0.5) %>% 
    layer_points() 
```


```{r}
#knit2html(input = "C:/Users/TaeHwan/Desktop/0. R/12. ggvis/ggvis_study.Rmd", output = "C:/Users/TaeHwan/Desktop/0. R/12. ggvis") 
```









