---
layout : post
title: "ggvis_study_2_[interactive]"
author: "ooDoo"
date: 2018-04-23
categories : ggvis
cover : /assets/article_images/title/instacode_sizedown.png
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# basic package
library(ggplot2)
library(ggthemr)
library(dplyr)
library(data.table)
library(readr)
library(ggvis)
library(knitr)


#setwd
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/12. ggvis")
```

# 1. Basic interactive controls
: 단순한 상수 값들을 변경 시키는 함수들
*모든 interactive function은 *`input_`*으로 시작한다*
Output function|Creates
:---:|:---:
•`input_slider()` | a slider (or a double-ended range slider)
•`input_checkbox()` | a check-box
•`input_checkboxgroup()` | a group of check boxes
•`input_numeric()`: a spin box
•`input_radiobuttons()` | pick one from a set options
•`input_select()` | create a drop-down text box
•`input_text()` | arbitrary text input

## 1) Make Basic sampel
 - step_1 : choose appropriate function 
 - step_2 : check the "inner option" fuction 
 - step_3 : make interactive condition using `input_` usage
 - step_4 : fill the neccasary condition at each interactive function
 
```{r}
mtcars %>%
  ggvis(~wt, ~mpg) %>%
  layer_smooths(span = input_slider(0.5, 1, value = 1)) %>%
  layer_points(size := input_slider(100, 1000, value = 100))
```

```{r}
# using 2 controls
mtcars %>% 
    ggvis(x = ~wt) %>%
    layer_densities(             # step_1 : choose appropriate function 
        adjust = input_slider(   # step_2 : check the "inner option" fuction // # step_3 : make interactive condition using `input_` usage
           min =  .1,            # step_4 : fill the neccasary condition at each interactive function
           max =  2,
           value = 1,
           step = .1, 
           label = "Bandwidth adjustment"),     
        kernel = input_select(
            c("Gaussian" = "gaussian",
              "Epanechnikov" = "epanechnikov",
              "Rectangular" = "rectangular",
              "Triangular" = "triangular",
              "Biweight" = "biweight",
              "Cosine" = "cosine",
              "Optcosine" = "optcosine"),
            label = "Kernel")
        )
```



# 2. Arguments 
 : 모든 `input_` 함수는 조금씩 그 타입은 다르지만, 공통적으로 세가지 arguments를 공유하고 있다. 
 - `label` : an infomative text label displayed next to the control 
 - `id` : a unique identifier for the control (this is randomly assigned and you should only need to override in execption circumstances)
 - `map` : a function that enables you to remap the output of the input to something appropriate for your graphic
  
```{r}
input_slider(min = -5, max = 5,
             label = "lambda",  # just informative text label
             map = function(x) 10 ^ x) # using `map', translate the natural number to 10^x 
```

`map` 을 활용하여, 표면적으로 입력되는 값을 내부적으로 변환하여 도표상의 유의미한 값으로 변형가능하다. 예를 들어 많은 통계 모델의 매개 변수가 로그 눈금에 가장 잘 표현됩니다. 슬라이더와 함께 맵을 사용하면 단일 슬라이더에서 여러 단계로 쉽게 액세스 할 수 있습니다.


# 3. Multiple OutPuts
: Interactive input 

## 1) Use the regular Property inheritance
: 일반 ggvis함수 안의 속성을 활용
```{r}
mtcars %>%
  ggvis(~wt, ~mpg, size := input_slider(10, 1000)) %>%
  layer_points(fill := "red") %>%
  layer_points(stroke := "black", fill := NA)
```


## 2) Create the input and assign it to a variable
: input목적의 객체를 생성하여 해당 객체에 변수 부여 방식 
```{r}
slider <- input_slider(10, 1000) 
mtcars %>%
    ggvis(~wt, ~mpg) %>%
    layer_points(fill := "red", size := slider) %>%
    layer_points(stroke := "black", fill := NA, size := slider)
```

## 3) compare the way
```{r}
slider <- input_slider(10, 1000)
mtcars %>% ggvis(~wt, ~mpg) %>%
  layer_points(size := slider) %>%  # without `fill` option, size means the stroke size
  layer_points(fill := "red", opacity := 0.5, size := slider)
# one slider is created and used for both layers
# it controls the size of both the red and the black points. 
```

```{r}
slider_1 <- input_slider(10, 1000)
slider_2 <- input_slider(10, 1000)
mtcars %>% ggvis(~wt, ~mpg) %>%
  layer_points(size := slider_1) %>% 
  layer_points(fill := "red", opacity := 0.5, size := slider_2)
```

```{r}
mtcars %>%
    ggvis(~wt, ~mpg) %>%
    layer_points(size := input_slider(100, 1000, label = "black")) %>%
    layer_points(fill := "red", size := input_slider(100, 1000, label = "red"))
# you get two independent sliders 
# which allow you to control the size of the red and black points independently.
```
:2개 이상의 input값을 주고 싶을 경우, 위와 같이 함수 내부에 각각의 input값을 주거나, 각각의 개별 input용 객체를 주어 이를 구별해주어야 한다.















