---
layout : post
title: "ggvis_study"
author: "ooDoo"
date: 2018-04-04
categories : ggvis
cover : /assets/article_images/title/instacode_sizedown.png
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# basic package
library(ggplot2)
library(ggthemr)
library(dplyr)
library(data.table)
library(readr)
library(ggvis)
library(knitr)


# install the latest development version 
# install.packages("devtools")
#devtools::install_github("hadley/lazyeval", build_vignettes = FALSE)
#devtools::install_github("hadley/dplyr", build_vignettes = FALSE)
#devtools::install_github("rstudio/ggvis", build_vignettes = FALSE)

#setwd
knitr::opts_knit$set(root.dir = "C:/Users/TaeHwan/Desktop/0. R/12. ggvis")
```

# 1. Dive into plotting with `ggvis`

## 1) basic Usage
```{r}
layer_points(ggvis(mtcars, x = ~wt, y = ~mpg))
```

```{r}
head(mtcars)
```


## 2) Using `dplyr`
```{r}
library(dplyr)
mtcars %>%
    mutate(disp = disp / 61.0237) %>% # convert engine displacment to litres
    ggvis(x = ~mpg, y = ~disp) %>%
    layer_points() 
```
*변수 앞에 "~"를 붙이는 이유*
 : ggvis안에서 사용하려는 변수는 실제 벡터 혙태로 저장 되어있는 변수가 아닌, 해당 데이터셋에서만 존재하는 컬럼이기에 이를 구분해 주기 위해서 반드시 "~"를 앞에 붙여야 한다. 
 
## 3) Mapping tools
 - `fill`
 - `stroke` 
 - `size`
 - `shape`
 
### (1) fill 
```{r}
# factors
mtcars %>% 
    ggvis(~mpg, ~disp, fill = ~as.factor(vs)) %>% 
    layer_points()

# numeric
mtcars %>% 
    ggvis(~mpg, ~disp, fill = ~qsec) %>% 
    layer_points()

# fixed colour
mtcars %>% 
    ggvis(~mpg, ~disp, fill := "skyblue") %>% 
    layer_points()
```
: same as ggplot's usage, but If you want to make the points a fixed colour or size, you need to use `:=` instead of `=`. 
 
### (2) stroke 
```{r}
# setting the stroke color using varialbe
mtcars %>%
    ggvis(~mpg, ~disp, stroke = ~vs) %>%
    layer_points()

# setting the stroke color using the fixed colour 
mtcars %>%
    ggvis(~mpg, ~disp, stroke := "black") %>%
    layer_points()
```
 
### (3) size
```{r}
mtcars %>%
    ggvis(~mpg, ~disp, size = ~vs) %>% 
    layer_points()
```
 

### (4) shape
```{r}
# shape  
mtcars %>% 
    ggvis(~mpg, ~disp, shape := "diamond") %>%
    layer_points() 

# shape differently as variable
mtcars %>% 
    ggvis(~mpg, ~disp, shape = ~factor(cyl)) %>%
    layer_points() 

# shape and color
mtcars %>% 
    ggvis(~mpg, ~disp, shape = ~factor(cyl), fill = ~as.factor(cyl)) %>%
    layer_points() 
```
*i don't know how to readjust the legend in ggvis yet*

 
### (5) opacity(alpha value in ggplot)
```{r}
mtcars %>% 
    ggvis(~wt, ~mpg, size := 300, opacity := 0.4) %>%
    layer_points()
```
 
 
#2. Interaction_using mouse
## (1) input_slider() 
### (1) control the size and opacity 
```{r}
mtcars %>% 
  ggvis(~wt, ~mpg, 
    size := input_slider(10, 100),
    opacity := input_slider(0, 1)) %>% 
  layer_points()
```

*the result gonna show on the *Viewer of Rstudio
if we want pass the next step, we have to quit the result such as shiny-apps

### (2) width and centers of histogram bins
```{r}
mtcars %>% 
    ggvis(~wt) %>% # since histogram only takes list of data type, indexing the value as above using "~""
    layer_histograms(width = input_slider(0, 4, step = 0.10, label = "width"),
                     center = input_slider(0, 2, step = 0.05, label = "center"))
```


## 2) input_checkbox
```{r}
mtcars %>% 
    ggvis(~wt) %>% 
    layer_histograms(width = input_slider(0, 4, step = 0.10, label = "width"),
                     center = input_slider(0, 2, step = 0.05, label = "center"))
    
```




## 3) Interaction_using keyboard 
```{r}
keys_s <- left_right(10, 1000, step = 50)
mtcars %>%
    ggvis(~wt, ~mpg, size := keys_s, opacity := 0.5) %>% 
    layer_points() 
```

## 4) etc : Tooltip
```{r}
mtcars %>%
    ggvis(x = ~wt, y = ~mpg) %>%
    layer_points() %>%
    add_tooltip(function(df) df$wt)
```
※tooltip : 포인트에 커서를 대면, 해당 포인트의 특정 값을 보여주는 기능


# 3. Layers
 : layers can be roughly categorised into two types.
- simple layer : primitives like points, line and rectangles
- Compound layer : combine data transformations with one or more simple layers

## 1) Simple Layer 
### (1) Point Layer : `layer_point()`
*option* : `x`,`y`, `shape`, `stroke`, `fill`, `strokeOpacity`, `fillOpacity`, `Opacity`
```{r}
mtcars %>%
    ggvis(x = ~wt, y = ~mpg) %>%
    layer_points(shape := "diamond", fill := "royalblue", opacity := 0.5)
```

### (2) Patys and Polygons : `layer_paths()`
```{r}
df <- data.frame(x = 1:10, y = round(runif(10),2))
df %>%
    ggvis(~x, ~y) %>%
    layer_paths(stroke := "pink")
```

*if you supply a* `fill`, *you'll get a polygon*
```{r}
df <- data.frame(x = 1:10, y = round(runif(10),2))
df %>%
    ggvis(~x, ~y) %>%
    layer_paths(stroke := "pink", fill := "skyblue")
```

```{r}
t <- seq(0, 2 * pi, length = 100)
df <- data.frame(x = sin(t), y = cos(t))
df %>%
    ggvis(~x, ~y) %>%
    layer_points() %>%
    layer_paths(fill := "blueviolet" , opacity := 0.5)
```

### (3) Filled area : `layer_ribbons()`
: use properties `y` and `y2` to control the extent of the area.
#### (a) fill the line up
```{r}
df <- data.frame(x = 1:10, y = runif(10))
df %>%
    ggvis(~x, ~y) %>%
    layer_paths(stroke := "red") %>%
    layer_ribbons(fill := "deepskyblue", opacity := 0.5)
```

#### (b) fill a limited area : using `y2`
```{r}
df %>%
    ggvis(x = ~x,
          y = ~y +0.1,
          y2 = ~y -0.1)%>%
    layer_ribbons(fill := "deepskyblue", opacity := 0.5)
```

### (4) Rectangles
```{r}
set.seed(1014)
df <- data.frame(x1 = runif(5),  x2 =runif(5), y1 = runif(5), y2 = runif(5))
df %>%
    ggvis(~x1, ~y1, x2 = ~x2, y2 = ~y2, fillOpacity := 0.1) %>%
    layer_rects()
```
※ difference btwn `fillOpacity`and `opacity`
- `fillOpacity` : make opacity only inside without stroke
- `opacity` : make opacity everything

### (5) text : layer_text()
- `text` : text (the label), 
- `dx` and `dy` : margin in pixels between text and anchor point
- `angle` : rotate the text
- `font` : font name
- `fontSize` : size in pixels
- `fontWeight`: e.g. bold or normal
- `fontStyle` : e.g. italic or normal
```{r}
df <- data.frame(x = 3:1, y = c(1, 3, 2), # point
                 label = c("a", "b", "c")) # text
df
df %>% 
    ggvis(x = ~x, y =~y, # point
          text := ~label) %>% # text
    layer_text(fontSize = ~x,
               angle := 90,
               fontWeight := "bold")
```


## 2) Compound Layer
### (1) Layer_lines()
 : automatically orders by the x variable

```{r}
t <- seq(0, 2 * pi, length = 20)
df <- data.frame(x = sin(t), y = cos(t))

# previous way using layer_paths
df %>%
    ggvis(~x, ~y) %>%
    layer_paths() 

# new way using layer_lines()
df %>%
    ggvis(~x, ~y) %>%
    layer_lines()

# arrnage + layer_paths
df %>%
    ggvis(~x, ~y) %>%
    arrange(x) %>%
    layer_paths()
df %>%
    ggvis(~x, ~y) %>%
    arrange(y) %>%
    layer_paths()
```
check out the difference btwn paths and lines
 => `layer_lines()` is equivalent to `arrange()` + `layer_paths()`
 
### (2) layer_histograms() & layer_freqpolys()
Both layers first bin the data with `compute_bin()` then display the results with either rects or lines.
```{r}
# layer_histograms()
mtcars %>%
    ggvis(~mpg) %>%
    layer_histograms()

# layer_freqpolys()
mtcars %>%
    ggvis(~mpg) %>%
    layer_freqpolys()
```

### (3) layer_smooths() 
: fits a smooth model to the data and displays predictions with a line. it's used to highhlight the trend in noisy data
```{r}
mtcars %>%
    ggvis(~wt, ~mpg) %>%
    layer_points(fill := "deeppink", opacity := 0.5) %>%
    layer_smooths(opacity := 0.5)

# control the degree of wiggliness with the span parameter
span <- input_slider(0.2, 1, value = 0.75)
mtcars %>%
    ggvis(~wt, ~mpg) %>%
    layer_points(fill := "deeppink", opacity := 0.5) %>%
    layer_smooths(span = span)
```


#4. Multiple layers
```{r}
mtcars %>% 
  ggvis(~wt, ~mpg) %>% 
  layer_smooths() %>% 
  layer_points()

mtcars %>% ggvis(~wt, ~mpg) %>%
    layer_points(fill := "black", opacity := 0.5) %>%
    layer_smooths(span = 1, stroke := "deepskyblue") %>% # underfitting
    layer_smooths(span = 0.3, stroke := "deeppink")      # overfitting
```









 




